Inferring Invariants of Distributed Programs

### 2015-05-01 Doc/approach.tex
changing dump to collect

Rather than dumping state at all program points we expect the
developer to mark interesting program points using annotations. The
program state will be dumped at only these annotated points. This will
also help to narrow down the focus to points that are identified by
the developer as interesting points without wasting resources
analyzing useless program points. The annotations will be identified
by the parser at the instrumentation phase and re-written to include
statements which will write the values of variable to a file when the
program reaches that point in the runtime. Since there can be multiple points annotated in a program by a
developer, vector clocks will be used to partially order annotation
pairs in the two programs.% This will also help to invalidate
% annotations inserted at irrelevant locations by the developer.

>>>>

Rather than recording state at all program points we expect the
developer to mark interesting program points using annotations. In our implementation developers need to put a comment \texttt{//@dump} after the program point. The
program state will be collected at only these annotated points. This will
also help to narrow down the focus to points that are identified by
the developer as interesting points without wasting resources
analyzing useless program points. The annotations will be identified
by the parser at the instrumentation phase and re-written to include
statements which will write the values of variable to a file when the
program reaches that point in the runtime. Since there can be multiple points annotated in a program by a
developer, vector clocks will be used to partially order annotation
pairs in the two programs.% This will also help to invalidate
% annotations inserted at irrelevant locations by the developer.
